Illustrating Model Properties

### 2024-06-25 model.qmd

# manually place legends
split_legends(
  axes=axes[0,0],
  titles=["ipsi N0", "ipsi LNL III"],
  locs=[(0.3, 0.99), (0.5, 0.55)],
)
split_legends(
  axes=axes[0,1],
  titles=["ipsi N0", "ipsi LNL III"],
  locs=[(0.3, 0.99), (0.5, 0.55)],
)
split_legends(
  axes=axes[1,0],
  titles=["ipsi N0", "ipsi LNL III"],
  locs=[(0.16, 0.99), (0.53, 0.55)],
)
split_legends(
  axes=axes[1,1],
  titles=["ipsi N0", "ipsi LNL III"],
  locs=[(0.13, 0.55), (0.5, 0.99)],
)

@@

all_false = {lnl: False for lnl in ["I", "II", "III", "IV", "V"]}

@@

ax[1].set_yticks([])
ax[1].set_xticks(np.linspace(0, 15, 6))

ax[2].set_yticks([])
ax[2].set_xticks(np.linspace(0, 15, 6))

>>>>

# manually place legends
split_legends(
  axes=axes[0,0],
  titles=["ipsi LNLs I-V healthy", "ipsi LNL III"],
  locs=[(0.3, 0.99), (0.5, 0.55)],
)
split_legends(
  axes=axes[0,1],
  titles=["ipsi LNLs I-V healthy", "ipsi LNL III"],
  locs=[(0.3, 0.99), (0.5, 0.55)],
)
split_legends(
  axes=axes[1,0],
  titles=["ipsi LNLs I-V healthy", "ipsi LNL III"],
  locs=[(0.16, 0.99), (0.53, 0.55)],
)
split_legends(
  axes=axes[1,1],
  titles=["ipsi LNLs I-V healthy", "ipsi LNL III"],
  locs=[(0.13, 0.55), (0.5, 0.99)],
)

@@

all_false = {lnl: False for lnl in ["I", "II", "III", "IV", "V", "VII"]}
all_true = {lnl: True for lnl in ["I", "II", "III", "IV", "V", "VII"]}

@@

scenario = Scenario(
  t_stages=["early"],
  midext=True,
  diagnosis={
    "ipsi": {"CT": all_false},
    "contra": {"CT": all_false},
  },
  involvement={"contra": {"III": True}},
)
contents.append(Histogram.from_hdf5(
  filename=paths.model_dir / "full" / "risks.hdf5",
  dataname=scenario.md5_hash("risks"),
  color=COLORS["green"],
  label="early, mid. ext.; N0",
))

scenario = Scenario(
  t_stages=["late"],
  midext=True,
  diagnosis={
    "ipsi": {"CT": all_false},
    "contra": {"CT": all_false},
  },
  involvement={"contra": {"III": True}},
)
contents.append(Histogram.from_hdf5(
  filename=paths.model_dir / "full" / "risks.hdf5",
  dataname=scenario.md5_hash("risks"),
  color=COLORS["blue"],
  label="adv., mid. ext.; N0",
))

scenario = Scenario(
  t_stages=["late"],
  midext=True,
  diagnosis={
    "ipsi": {"CT": {"III": True}},
    "contra": {"CT": {"I": False, "II": True, "III": False, "IV": False, "V": False, "VII": False}},
  },
  involvement={"contra": {"III": True}},
)
contents.append(Histogram.from_hdf5(
  filename=paths.model_dir / "full" / "risks.hdf5",
  dataname=scenario.md5_hash("risks"),
  color=COLORS["red"],
  label="adv., mid. ext.;\nipsi LNL III & contra LNL II",
))

draw(ax[1], contents, xlims=(0., 8.))
ax[1].legend(labelspacing=0.1)
ax[1].set_xlabel("risk [%]")
ax[1].set_yticks([])
ax[1].set_xticks(np.linspace(0, 8, 9))
ax[1].set_title("Contralateral LNL III")

# contra LNL IV
contents = []

scenario = Scenario(
  t_stages=["late"],
  midext=True,
  diagnosis={
    "ipsi": {"CT": {"III": True}},
    "contra": {"CT": all_false},
  },
  involvement={"contra": {"IV": True}},
)
contents.append(Histogram.from_hdf5(
  filename=paths.model_dir / "full" / "risks.hdf5",
  dataname=scenario.md5_hash("risks"),
  color=COLORS["green"],
  label="adv., mid. ext.; ipsi LNL III",
))

scenario = Scenario(
  t_stages=["late"],
  midext=True,
  diagnosis={
    "ipsi": {"CT": all_true},
    "contra": {"CT": {"I": True, "II": True, "III": True, "IV": False, "V": False, "VII": False}},
  },
  involvement={"contra": {"IV": True}},
)
contents.append(Histogram.from_hdf5(
  filename=paths.model_dir / "full" / "risks.hdf5",
  dataname=scenario.md5_hash("risks"),
  color=COLORS["red"],
  label="adv., mid. ext.;\nsevere bilat. inv.",
))

draw(ax[2], contents, xlims=(0., 5.))
ax[2].legend(labelspacing=0.1)
ax[2].set_xlabel("risk [%]")
ax[2].set_yticks([])
ax[2].set_xticks(np.linspace(0, 5, 6))
ax[2].set_title("Contralateral LNL IV")
